Evaluation of probabilistic photometric redshift estimation approaches for \textsc{LSST}

### 2019-11-12 paper/tex/results.tex
change line format on Figures 3 and A2 and modify legends, add plot script

\begin{figure*}
\centering
\includegraphics[width=0.74\textwidth]{fig/KSvsCvMvsAD_PIT_withbootstrap.jpg}
\caption{A visualization of the Kolmogorov-Smirnoff (KS, blue diamond), Cramer-von Mises (CvM, black star), and Anderson-Darling (AD, red asterisk) statistics for the PIT distributions.
There is generally good agreement between these statistics, with differences corresponding to the codes with outstanding catastrophic outlier rates, a reflection in the differences in how each statistic weights the tails of the distribution.
Horizontal lines indicate the level of uncertainty found by bootstrapping a training set sample of 30,000 galaxies using \trainz; none of the codes reach this conservative ideal floor in expected uncertainty.}
\label{fig:pit_stats}
\end{figure*}

@@

Of the metrics we were able to consider in this experiment, \textbf{the CDE Loss is the only metric that can appropriately penalize the pathological\trainz}.
Additionally, it favors \cmnn\ and \flexzboost, the latter of which is optimized for this metric.

>>>>

\begin{figure*}
\centering
\includegraphics[width=0.74\textwidth]{fig/KSvsCvMvsAD_PIT_withnull_jpg.jpg}
\caption{A visualization of the Kolmogorov-Smirnoff (KS, blue diamond), Cramer-von Mises (CvM, black star), and Anderson-Darling (AD, red asterisk) statistics for the PIT distributions.
There is generally good agreement between these statistics, with differences corresponding to the codes with outstanding catastrophic outlier rates, a reflection in the differences in how each statistic weights the tails of the distribution.
Horizontal lines indicate the level of uncertainty found by bootstrapping a training set sample of 30,000 galaxies using \trainz; none of the codes reach this conservative ideal floor in expected uncertainty.}
\label{fig:pit_stats}
\end{figure*}

@@

Of the metrics we were able to consider in this experiment, \textbf{the CDE Loss is the only metric that can appropriately penalize the pathological \trainz}.
Additionally, it favors \cmnn\ and \flexzboost, the latter of which is optimized for this metric.
